Create datasets: frog survival, presence/absence of life stages indicative of reproductive success

### 2023-05-18 code/translocation_survival_createdata.Rmd
Minor edits to comments

frog_counts <- sites %>% 
  inner_join(visit_ves, by = "site_id") %>% 
  inner_join(survey_ves, by = "visit_id") %>% 
  filter(survey_type == "visual") %>% 
  left_join(visual_survey_ves, by = "survey_id") %>% 
  select(siteid_alt, visit_date, visual_life_stage, location, count) %>% 
  mutate(visit_year = year(visit_date), .after = visit_date) %>% 
  group_by(siteid_alt, visit_date, visit_year, visual_life_stage) %>% 
  summarize(count_total = sum(count)) %>% 
  group_by(siteid_alt, visit_year, visual_life_stage) %>% 
  summarize(count_max = max(count_total)) %>% 
  ungroup() %>% 
  complete(visual_life_stage, # cross all possible life_stage values with the unique pairs of (siteid_alt, visit_year) that exist in the data 
           nesting(siteid_alt, visit_year),
           fill = list(count_max = 0)) %>% 
  select(siteid_alt, visit_year, visual_life_stage, count_max) %>% 
  filter(!is.na(visual_life_stage)) %>% 
  inner_join(relocate_ves, by = "siteid_alt") %>% 
  select(-release_date_min) %>% 
  filter(visit_year > release_year) # Exclude surveys/counts made in the year of translocation (before presence of tadpoles is possible)

@@

frog_captures <- sites %>% 
  inner_join(visit_cmr, by = "site_id") %>% 
  inner_join(survey_cmr, by = "visit_id") %>% 
  filter(survey_type == "cmr" |
         survey_type == "visual") %>% # Include CMR and VES records to ensure inclusion of all survey dates. Survey without RAMU detections typically recorded as VES. 
  left_join(capture_survey_cmr, by = "survey_id") %>% 
  select(siteid_alt, visit_date, survey_type, pit_tag_ref, tag_new) %>% 
  mutate(visit_year = year(visit_date), .after = visit_date) %>% 
  distinct(siteid_alt, visit_year, pit_tag_ref) %>% 
  group_by(siteid_alt, visit_year) %>% 
  summarize(recruits = sum(!is.na(pit_tag_ref))) %>%  # !is.na() converts pit_tag_ref records to TRUE/FALSE. sum() treats TRUE as 1/FALSE as 0, so sum is count of not NA values
  ungroup() %>% 
  inner_join(relocate_cmr, by = "siteid_alt") %>% 
  select(-release_date_min) %>% 
  filter(visit_year > (release_year + 2)) # Exclude counts made in first 3 years after translocation (before recruitment is possible)

>>>>

frog_counts <- sites %>% 
  inner_join(visit_ves, by = "site_id") %>% 
  inner_join(survey_ves, by = "visit_id") %>% 
  filter(survey_type == "visual") %>% 
  left_join(visual_survey_ves, by = "survey_id") %>% 
  select(siteid_alt, visit_date, visual_life_stage, location, count) %>% 
  mutate(visit_year = year(visit_date), .after = visit_date) %>% 
  group_by(siteid_alt, visit_date, visit_year, visual_life_stage) %>% 
  summarize(count_total = sum(count)) %>% 
  group_by(siteid_alt, visit_year, visual_life_stage) %>% 
  summarize(count_max = max(count_total)) %>% 
  ungroup() %>% 
  complete(visual_life_stage, # cross all possible life_stage values with the unique pairs of (siteid_alt, visit_year) that exist in the data 
           nesting(siteid_alt, visit_year),
           fill = list(count_max = 0)) %>% 
  select(siteid_alt, visit_year, visual_life_stage, count_max) %>% 
  filter(!is.na(visual_life_stage)) %>% 
  inner_join(relocate_ves, by = "siteid_alt") %>% 
  select(-release_date_min) %>% 
  filter(visit_year > release_year) # Exclude surveys/counts made in the year of first translocation (before presence of tadpoles is possible)

@@

frog_captures <- sites %>% 
  inner_join(visit_cmr, by = "site_id") %>% 
  inner_join(survey_cmr, by = "visit_id") %>% 
  filter(survey_type == "cmr" |
         survey_type == "visual") %>% # Include CMR and VES records to ensure inclusion of all survey dates. Survey without RAMU detections typically recorded as VES. 
  left_join(capture_survey_cmr, by = "survey_id") %>% 
  select(siteid_alt, visit_date, survey_type, pit_tag_ref, tag_new) %>% 
  mutate(visit_year = year(visit_date), .after = visit_date) %>% 
  distinct(siteid_alt, visit_year, pit_tag_ref) %>% 
  group_by(siteid_alt, visit_year) %>% 
  summarize(recruits = sum(!is.na(pit_tag_ref))) %>%  # !is.na() converts pit_tag_ref records to TRUE/FALSE. sum() treats TRUE as 1/FALSE as 0, so sum is count of not NA values
  ungroup() %>% 
  inner_join(relocate_cmr, by = "siteid_alt") %>% 
  select(-release_date_min) %>% 
  filter(visit_year > (release_year + 2)) # Exclude counts made in first 3 years after initial translocation (before recruitment is possible)
